CF Registry Analysis

### 2022-09-06 Christine Chan/CF Registry/cf_registry_analysis.Rmd
Update cf_registry_analysis.Rmd

```{r}
# Read in CSVs
df = read.csv("./Data_Raw/CFF19_encountersMerged_Del1.csv")
annual = read.csv("./Data_Raw/CFF19_Annualized_Del1.csv")
colnames(annual)[colnames(annual)=="ReviewYear"] = "reviewyear"
# # Merge
# df = df.join(annual, on=['eDWID', 'reviewyear'],how="left")
# # Group years by 2003-2009, 2010-2013, and 2014-2018
# df["Period"] = pd.cut(df["reviewyear"], [2003, 2009, 2013, 2018])
# # Small dataframe for checking
# test = df.iloc[0:1000,:]
# test.to_csv("~/test.csv",index=False)
```

>>>>

```{r cache=TRUE}
# Read in CSVs
df = read.csv("./Data_Raw/CFF19_encountersMerged_Del1.csv")
annual = read.csv("./Data_Raw/CFF19_Annualized_Del1.csv")
colnames(annual)[colnames(annual)=="ReviewYear"] = "reviewyear"
demo = read.csv("./Data_Raw/CFF19_DemogCFDiag_Del1.csv")
# Combine and format demographics columns 
demo$Race = apply(demo,1,function(r){
  race = r[paste0("Race",1:6)]
  race = as.numeric(which(race == 1))
  race = paste(race,collapse = ", ")
})
demo$Race[grep(", ",demo$Race)] = "More Than One"
demo$Race = factor(demo$Race,levels = c(1:6,"More Than One"),
                   labels = c("White","Black or African American",
                              "American Indian or Alaska Native","Asian",
                              "Native Hawaiian or Other Pacific Islander",
                              "Some other race","More Than One"))
demo$Hispanicrace = factor(demo$Hispanicrace,levels = 1:2,
                           labels = c("Yes","No"))
# Merge
df = left_join(df,annual, by=c('eDWID', 'reviewyear'))
df = left_join(df,demo,by = "eDWID")
# Group years by 2003-2009, 2010-2013, and 2014-2018
df$Period = cut(df$reviewyear,
                breaks =c(2002, 2009, 2013, 2018),
                labels = c("2003 - 2009","2010 - 2013","2014 - 2018"))
df$smoking = factor(df$smoking,levels = 1:4,labels = c("No",
                                                       "Occasionally",
                                                       "Yes, Regularly, less than 1 ppd",
                                                       "Yes, Regularly, 1 ppd or more"),ordered = T)
df$second_smoke = factor(df$smoking,levels = 1:4,labels = c("No",
                                                            "Occasionally",
                                                            "Yes, Regularly, less than 1 ppd",
                                                            "Yes, Regularly, 1 ppd or more"),ordered = T)
# Factors
ed_levels = c("Less than High School",
              "High School diploma or equivalent",
              "Some College",
              "College Graduate",
              "Masters/Doctoral level degree")
df$patient_education = factor(df$patient_education,levels = c(1:5),
                              labels = ed_levels)
df$father_education = factor(df$father_education,levels = c(1:5),
                             labels = ed_levels)
df$mother_education = factor(df$mother_education,levels = c(1:5),
                             labels = ed_levels)
df$spouse_education = factor(df$spouse_education,levels = c(1:5),
                             labels = ed_levels)
df$pregnant = factor(df$pregnant,levels = 0:1,labels = c("No","Yes"),ordered = T)
# Combine education checkboxes
cl = makeCluster(detectCores()*0.5,type = "FORK")
df$employment = parApply(cl,df,1,function(r){
  emp = r[paste0("employment",1:7)]
  emp = as.numeric(emp)
  if(all(is.na(emp) | emp == 0)){
    return(NA)
  } else {
    emp = as.numeric(emp)
    emp = which(emp == 1)
    emp = paste(emp,collapse = ", ")
    return(emp)
  }
})
stopC
df$employment = sub("1","Part Time",df$employment)
df$employment = sub("2","Full time homemaker",df$employment)
df$employment = sub("3","Full time employment",df$employment)
df$employment = sub("4","Unemployed",df$employment)
df$employment = sub("5","Student",df$employment)
df$employment = sub("6","Disabled",df$employment)
df$employment = sub("7","Retired",df$employment)
df$employment = as.factor(df$employment)
# Small dataframe for checking
test = df[1:1000,]
write.csv(test,"~/test.csv",row.names = F)
```

# Table 1: Participant characteristics at last visit in time period

```{r warning=FALSE}
t1_df = df %>% group_by(eDWID,Period) %>% 
  summarise(Age = max(Age_YrEnd[is.finite(Age_YrEnd)]),Race = last(na.omit(Race)),
            Hispanic = last(na.omit(Hispanicrace)),Gender = last(na.omit(Gender)),
            `Patient Education` = last(na.omit(patient_education)),
            `Father Education` = last(na.omit(father_education)),
            `Mother Education` = last(na.omit(mother_education)),
            `Spouse Education` = last(na.omit(spouse_education)),
            `Marital Status` = last(na.omit(marital_status)),
            Employment = last(na.omit(employment)),
            Pregnancy = max(pregnant,na.rm = T)
  )
# Replace infinite values with missing
t1_df = data.frame(lapply(t1_df, function(c){
  c[is.infinite(c)] = NA
  return(c)
}))

cols = colnames(t1_df)[3:ncol(t1_df)]
t1 = tableby(as.formula(paste0("Period~",paste0("`",cols,"`",collapse = "+"))),
             data = t1_df)
```
